Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-03 analysis/paper/paper.Rmd
Reword statistical analysis findings for clarity

There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A; Table S3).

However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4).

The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6).

>>>>

The analysis for the effect of year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A; Table S3).

The null hypothesis that the year of publication had no effect on the availability of data was not rejected.
The analysis found that there was no effect of year of publication on the availability of data (Median = 0.08, 95% CI [-8.06e-03, 0.18]) with a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30) (Figure \@ref(fig:year-parameters)B, Table S4).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).

The analyses were undecided when predicting both the effects of the five-year impact factor on the availability of computational methods (code) and data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6).
